|

### 2021-06-29 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

---
title: |
  | Supporting Information for:
  | Emergent dual scaling of riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of Minnesota, St. Paul, MN 55108, USA]
- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
bibliography: reference.bib
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

>>>>

---
title: |
  ![](image/logo.png){width=4in}  
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
bibliography: reference.bib
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---
